%+----------------------------------------------------------------------------+
%| SLIDES: 
%| Chapter: Introduction  end -> lead to multisymplectic geometry
%| Author: Antonio miti
%| Event: Phd Colloquium - What is ... Geometric mechanics?
%+----------------------------------------------------------------------------+

%- HandOut Flag -----------------------------------------------------------------------------------------
\makeatletter
\@ifundefined{ifHandout}{%
  \expandafter\newif\csname ifHandout\endcsname
}{}
\makeatother

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,10pt]{standalone}   
%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue  

\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

	
%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}




%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}
\usetikzlibrary{positioning}




%---------------------------------------------------------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------------------------


%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Geometric Mechanics: Take Away Message}
	\begin{itemize}
		\item[•] \alert{States} are encoded by a \alert{symplectic manifold}.
		\begin{itemize}
			\item[-] Smooth manifolds arise naturally in the description of mechanical systems.
			\item[-] Constraints can be enforced intrinsically
			\item[-] Geo. Mech. yields an inherent intuition of diff. geom. structures.
		\end{itemize}
		\item<2->[•] \alert{Observables} quantities are encoded by \alert{smooth functions}.
		\begin{itemize}
			\item[-] The symplectic structure prescribe how to associate a vec. field to any observable.
			\item[-] Time evolution is obtained by integrating the flow along an Ham. v.f.
		\end{itemize}				
		\item<3->[•] \alert{Continuous symmetries} are encoded by \alert{symplectic Lie group actions}.
		\begin{itemize}
			\item[-] A relevant class of symmetries can be reconstructed from observables quantities via \emph{comomentum maps}.
			\item[-] Their importance lies in the existence of corresponding conserved quantities and the reduced description arising from them.
		\end{itemize}				
	\end{itemize}
	%Symplectic geometry is central
	\vfill
	%
	\onslide<4->{
		\begin{disclaimerbox}[we glossed on some technical details]
			\resizebox{.85\textwidth}{!}{
				\begin{columns}
					\begin{column}[T]{0.65\textwidth}
						\begin{itemize}
							\item[-] \color{black!80!white} Galilean / Special / General relativity (observer)
							\item[-] Holonomics / Non-holonomics constraints
							\item[-] Conservative / Dissipative system
							\item[-] Discrete / \alert{Continuous} degrees of freedom.
						\end{itemize}
					\end{column}					
					\begin{column}[T]{0.5\textwidth}
						\begin{itemize}
							\item[-] \color{black!80!white} Classical / Quantum observability
							\item[-] Lagrangian / Hamiltonian dynamics
							\item[-] Velocities $\neq$ Momenta
							\item[-] Local / Global flow integrability
						\end{itemize}
					\end{column}							
				\end{columns}
			}				
		\end{disclaimerbox}	
	}

\end{frame}
\note[itemize]{
	\item Symplectic geometric is central being the arena for describing many ideal systems.
	\item It can be extended and modified to take into account more realistic or general cases of study.

	\item geometry is an intrinsic part of mechanics. 
	The set of configurations has a natural geometric structure, constraints are automatically satisfied by this choice.
	\item {\bf describing states as points of a manifold is the principal premise of geometric mechanics.}
	\item Conf. space and Phase space are manifolds (a higher-dimensional generalization of surfaces)
	\item A large class of constraints can be enforced intrinsically by the topology (shape) of the manifold.


	\item an important trait of geometric mechanics is its intuitive nature: structures and time evolution of mechanical systems can be illustrated by visualizing configuration and phase space.
	Practically working in Geo. Mech. often means to exploit the inherent geometric intuition.
	
	\item an important characteristic is its emphasis on laying a rigorous mathematical foundation on which one can build upon mechanics. 
	While Newtonian mechanics is highly descriptive it does not reveal the underlying structure.
	In geo. mech. computations are structural arguments that provide insight into the fabric they represent. 

	\item Huge disclaimer: in the above presentation we glossed out on several details...

}

%-------------------------------------------------------------------------------------------------------------------------------------------------




%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t,fragile]{Going higher: multisymplectic geometry}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
	\end{block}
	\vfill	
	\begin{table}
		\only<2->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & \only<3->{multisymplectic manifold} \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & \only<3->{$L_\infty$-algebra} \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & 
            \only<3->{group actions admitting 
				\tikz[baseline,remember picture]{\node[rounded corners,
	                        fill=orange!10,draw=orange!30,anchor=base]            
	            			(target) {homotopy comomentum map};
	            }
            }
            \\
            \hline
  \multicolumn{1}{c}{}
            &  
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{\only<4->{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$}} 
		\end{tabular}
		}
	\end{table}		
	\vfill
	\onslide<4->{
		\begin{block}{Scope of the thesis}
			\begin{itemize}
				\item[$\bullet$] Develop theory of 
					\tikz[baseline,remember picture]{\node[rounded corners,
	                        fill=orange!10,draw=orange!30,anchor=base]            
	            			(base) {homotopy comomentum maps};
	            	}
	            \item[$\bullet$] produce new meaningful examples.
			\end{itemize}
		\end{block}
		%
        \begin{tikzpicture}[overlay,remember picture]
			\path[->]<4-> (base.east) edge[bend right](target.south east);
		\end{tikzpicture}
	}
	%
\end{frame}
\note[itemize]{
	\item a Keyword in my thesis was "multisymplectic", how does this generalization came out?
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics} 
	
	\item General ideas basic parallelisms with caveats
	\item caveat: points in multiphase spaces are not states
	\item the table hides the duality between geometric and algebraic approaches to the problem. 
}
%-------------------------------------------------------------------------------------------------------------------------------------------------












%----------------------------------------------------------------------------------------------------------------------------------
\end{document}
%----------------------------------------------------------------------------------------------------------------------------------







